Roster Review (Generic)

### 2019-06-05 rosterReview_generic.Rmd
Minor pos_zar bug fix

```{r}
# TODO find way to wrap these three views into one
rosters %>% 
  filter(grepl("Plouffe|Dorn",team)) %>% 
  select(team, manager, name_full, display_position, zar) %>% 
  arrange(zar %>% desc) %>% 
  View()
  # mutate(zar = janitor::round_half_up(zar)) %>% 
  # write_csv("data/tradeReview_20190423.csv")

rosters %>% 
  filter(grepl("Plouffe|Dorn",team)) %>% 
  ggplot(aes(x=team,y=zar,color=type)) +
  geom_jitter(aes(text=glue("{name_full} - {display_position}", color=type)), width=.2) +
  coord_flip() -> tv

@@

rosters %>% 
  filter(grepl("Dorn|process",team)) %>% 
  select(team, manager, name_full, display_position, zar) %>% 
  filter(grepl("Trout|Whitley|Cain|Price",name_full)) %>% 
  group_by(team) %>% 
  summarize(zar = sum(zar))

rosters %>% 
  filter(grepl("Dorn|process",team)) %>% 
  select(team, manager, name_full, display_position, war) %>% 
  filter(grepl("Trout|Whitley|Cain|Price",name_full))
```

@@

```{r}
#TODO move to separate research
#FIXME where is Robinson Chirinos?

@@

rosters_by_position %>% 
  full_join(pos_median_zar) %>% 
  mutate(pos_zar = zar + median_zar) -> rosters_by_position

>>>>

```{r}
# TODO find way to wrap these three views into one
rosters %>% 
  filter(grepl("Plouffe|Matter",team)) %>% 
  select(team, manager, name_full, display_position, zar, positions) %>% 
  arrange(zar %>% desc) %>% 
  View()
  # mutate(zar = janitor::round_half_up(zar)) %>% 
  # write_csv("data/tradeReview_20190423.csv")

rosters %>% 
  filter(grepl("Plouffe|Matter",team)) %>% 
  ggplot(aes(x=team,y=zar,color=type)) +
  geom_jitter(aes(text=glue("{name_full} - {display_position}", color=type)), width=.2) +
  coord_flip() -> tv

@@

rosters %>% 
  filter(grepl("Plouffe|Matter",team)) %>% 
  select(team, manager, name_full, display_position, zar) %>% 
  filter(grepl("Hicks|Muncy",name_full)) 
# %>%
#   group_by(team) %>%
#   summarize(zar = sum(zar))
```

@@

```{r}
#TODO move to separate research

@@

rosters_by_position %>% 
  full_join(pos_median_zar) %>% 
  mutate(pos_zar = zar - median_zar) -> rosters_by_position
